Semi-supervised author disambiguation of scientific publications

### 2015-07-16 paper.tex
autosave

Efforts and solutions to author disambiguation have been proposed from various
communities \citep{liu2014author}. On the one hand, libraries have maintained
authorship control through manual curation, either in a centralized way by
hiring collaborators or by developing services inviting authors to register
their publications themselves (e.g., Google Scholar, Inspire-HEP). Recently,
efforts started to assign persistent digital identifiers to researchers (e.g.,
ORCID, ResearchedID), with the further objective to embed these identifiers in
the submission workflow of publishers or repositeries (e.g., Elsevier, arXiv,
Inspire-HEP), thereby univocally solving any disambiguation issue. With the
large cost of centralized manual authorship control or until the larger
adoption of crowdsourced solutions, the impact of these efforts are
unfortunately limited by the efficiency, motivation and integrity of their
active contributors. For these reasons, fully automated machine learning-based
methods have been proposed during the past decade to provide less costly and
more efficient solutions to author disambiguation. In this work, ...

@@

\section{Related works}
\label{relate-works}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Phasellus malesuada
eleifend pretium. Nulla semper aliquam arcu vel euismod. Curabitur dapibus
tortor varius, pretium lectus at, tempus lectus. Mauris pellentesque, turpis
vitae vulputate auctor, enim metus hendrerit nulla, ac elementum felis leo in
nulla. Cras sed suscipit magna. Donec enim enim, egestas facilisis odio quis,
laoreet maximus ligula. Nam vel metus at enim venenatis fringilla. Fusce nisl
nunc, pellentesque eget arcu a, tempor interdum arcu. Duis non urna ligula.
Vivamus consequat cursus auctor.

>>>>

Efforts and solutions to author disambiguation have been proposed from various
communities \citep{liu2014author}. On the one hand, libraries have maintained
authorship control through manual curation, either in a centralized way by
hiring collaborators or by developing services inviting authors to register
their publications themselves (e.g., Google Scholar, Inspire-HEP). Recently,
efforts started to assign persistent digital identifiers to researchers (e.g.,
ORCID, ResearchedID), with the further objective to embed these identifiers in
the submission workflow of publishers or repositeries (e.g., Elsevier, arXiv,
Inspire-HEP), thereby univocally solving any disambiguation issue. With the
large cost of centralized manual authorship control or until the larger
adoption of crowdsourced solutions, the impact of these efforts are
unfortunately limited by the efficiency, motivation and integrity of their
active contributors. For these reasons, fully automated machine learning-based
methods have been proposed during the past decade \glnote{Add references} to provide less costly and
more efficient solutions to author disambiguation. In this work, our goal is to
explore and demonstrate how both approaches can coexist and benefit from each
other.  In particular, we study how curated data obtained through manual
curation (either centralized or crowdsourced) can be exploited (i) to learn an
accurate classifier for identifying corefering authors, (ii) to guide the
clustering of scientific publications by distinct authors in a semi-supervised
way and finally (iii) to match the resulting clusters with existing profiles.
Our analysis of parameters and features on this large training set reveal
that... \glnote{To be completed with actual results.}

The remaining of this report is structured as follows. In Section~\ref{related-works}, ...

@@

\section{Related works}
\label{related-works}
